Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-04-23 CONCUR2018/paper.tex
abstract

\begin{abstract} 
%
We present a sound and automated approach to synthesizing safe, digital,
observer-based controllers for physical plants represented as linear,
time-invariant models.  Models are defined as differential equations with
inputs, evolving over a continuous state space.  The synthesis accounts for
errors caused by the digitization effects introduced by the controller. 
We~use counterexample-guided inductive synthesis enhanced with abstraction
refinement and optimization, which allows us to start with a low-resolution
discretized model and find candidate solutions fast.  This model is refined
on demand.  Moreover, in order to improve our chances of finding a solution
even when considering coarse abstractions of the system, in each iteration
of the CEGIS loop we use matrix eigen-decomposition to optimize our
candidate.
%
%% Once we have a candidate, we use matrix eigen-decomposition
%% and objective functions to iteratively optimize it.
%Whenever the optimization is unable to yield further results, it feeds back to the
%synthesiser in a traditional CEGIS manner.
%
This design yields a significant speed-up compared to traditional CEGIS
(i.e., without abstraction refinement and optimization).  We~demonstrate the
practical value of this approach by automatically synthesizing safe
observer-based controllers for physical plant models from the digital
control literature.
%
\end{abstract}

>>>>

\begin{abstract} 
%
We present a sound and automated approach to synthesizing safe, digital,
observer-based controllers for physical plants represented as linear,
time-invariant models.  Models are defined as differential equations with
inputs, evolving over a continuous state space.  The synthesis accounts for
errors caused by the digitization effects introduced by the controller. 
We~use counterexample-guided inductive synthesis enhanced with abstraction
refinement and optimization, which allows us to start with a low-resolution
discretized model and to find candidate solutions fast, or to refine this model on demand.  
Moreover, in order to improve our chances of finding a solution
even when considering coarse abstractions of the system, 
 in each iteration  we 
%of the CEGIS loop we use matrix eigen-decomposition to 
optimize our candidate.
%
%% Once we have a candidate, we use matrix eigen-decomposition
%% and objective functions to iteratively optimize it.
%Whenever the optimization is unable to yield further results, it feeds back to the
%synthesiser in a traditional CEGIS manner.
%
This design yields a significant speed-up compared to traditional CEGIS
(i.e., without abstraction refinement or optimization).  We~demonstrate the
practical value of this approach by automatically synthesizing safe
observer-based controllers for physical plant models from the digital
control literature.
%
\end{abstract}
